---
title: "Mann-Kendall Test Report"
output: html_document
params: 
  output_dir: "[output_dir]"
  include_details: TRUE
  include_code: TRUE
  alpha: "[alpha]"
  outcome: "[outcome]"
  p_value: "[p_value]"
  s_statistic: "[s_statistic]"
  s_variance: "[s_variance]"
---

The **MK Test** is used to assess whether there is a statistically significant monotonic trend in a time series.
The test requires that when no trend is present, the data is independent and identically distributed.
In particular, the data must not be _autocorrelated_.

- Null Hypothesis: There is no monotonic trend.
- Alternative Hypothesis: There is a monotonic upwards or downwards trend.

<!-- Render additional details about the test. -->
```{r, child = if(include_details) 'mk-details.Rmd' }
```

## Results

<!-- Include code used to compute the results. -->

```{r, echo = FALSE, include = include_code } 
asis_output("### Code") 
```

```{r, file = "mk-test.R", include = include_code, eval = FALSE } 

```

<!-- Include the results. -->

## Statistics

- S-statistic: `r round(params$s_statistic, 2)`
- P-value: `r round(params$p_value, 3)`
- Significance level: `r params$alpha`

Given the test statistic and p-value, we *`r params$outcome`* the null hypothesis.
