---
title: "Moving Window Mann-Kendall Test Report"
output:
  html_document:
    css: ../styles.css
  html_notebook:
    css: ../styles.css
params: 
  output_dir: "[output_dir]"
  include_details: TRUE
  include_code: TRUE
  alpha: "[alpha]"
  reject: "[reject]"
  std: "[std]"
  s_statistic: "[s_statistic]"
  s_variance: "[s_variance]"
  p_value: "[p_value]"
  msg: "[msg]"
---

### Moving Window Mann-Kendall Test

The **MW-MK Test** is used to identify a statistically significant monotonic trend in the variances of an AMS time series.

- Null hypothesis: There is no significant trend in the variance of the AMS.
- Alternative hypothesis: There is a significant trend in the variance of the AMS.
   
<!-- Render additional details about the test. -->
```{r, child = if(include_details) 'mwmk-details.Rmd' }
```

<!-- Include the results. -->

#### Results

`r params$msg`

Additional information:

- S-statistic: `r round(params$s_statistic, 2)`
- S-statistic variance: `r format(params$s_variance, scientific = TRUE, digits = 3)`

<!-- Include code used to compute the results. -->

```{r, echo = FALSE, include = include_code } 
asis_output("#### Code") 
```

```{r, file = "mwmk-test.R", include = include_code, eval = FALSE } 

```

