---
title: "Sen's Trend Estimator Report"
output:
  html_document:
    css: ../styles.css
  html_notebook:
    css: ../styles.css
params: 
  data_type: "[data_type]"
  output_dir: "[output_dir]"
  include_details: TRUE
  include_code: TRUE
  alpha: "[alpha]"
  sens_slope: "[sens_slope]"
  sens_intercept: "[sens_intercept]"
  residuals: "[residuals]"
  p_value: "[p_value]"
  reject: "[reject]"
  msg: "[msg]"
---

### Sen's Trend Estimator

**Dataset**: AMS `r params$data_type`.

**Sen's Trend Estimator** is used to estimate the slope of a regression line.
Unlike [Least Squares](https://en.wikipedia.org/wiki/Least_squares), Sen's trend estimator uses a non-parametric approach which makes it robust to outliers.

After computing the regression line using Sen's trend estimator, we use the **Runs Test** to determine whether the residuals from the regression are random.
If the Runs test identifies a non-random pattern in the residuals, it is a strong indication that the non-stationarity in the data is non-linear.

- Null hypothesis: The residuals are distributed randomly.
- Alternative hypothesis: The residuals *are not* distributed randomly.

<!-- Render additional details about the test. -->
```{r, child = if(params$include_details) 'sens-details.Rmd' }
```
<!-- Include the results. -->

#### Results

`r params$msg`

<!-- Render the figure. -->

#### Figure

```{r, echo = FALSE, out.width = "720px", fig.align = "center"}
file_name <- glue("img/sens-{params$data_type}-estimator.png")
include_graphics(file.path(params$output_dir, file_name))
```

<!-- Include code used to compute the results. -->

```{r, echo = FALSE, include = params$include_code } 
asis_output("#### Test Code") 
```

```{r, file = "sens-estimator.R", include = params$include_code, eval = FALSE } 

```

```{r, echo = FALSE, include = params$include_code } 
asis_output("#### Plotting Code") 
```

```{r, file = "sens-plot.R", include = params$include_code, eval = FALSE } 

```
