---
title: "KPSS Test Report"
output: html_document
params: 
  output_dir: "[output_dir]"
  include_details: TRUE
  include_code: TRUE
  alpha: "[alpha]"
  outcome: "[outcome]"
  p_value: "[p_value]"
---

The **KPSS Test** is used to identify if an autoregressive time series has a _unit root_.

- Null Hypothesis: $\sigma^2 = 0$, so the time series does not have a unit root ($\mu_{t}$ constant).
- Alternative Hypothesis: $\sigma^2 > 0$, so the time series has a unit root (through $\mu_{t}$).


<!-- Render additional details about the test. -->
```{r, child = if(include_details) 'kpss-details.Rmd' }
```

## Results

<!-- Include code used to compute the results. -->

```{r, echo = FALSE, include = include_code } 
asis_output("### Code") 
```

```{r, file = "kpss-test.R", include = include_code, eval = FALSE } 

```

<!-- Include the results. -->

### Statistics

- P-value: `r round(params$p_value, 3)`
- Significance level: `r params$alpha`

Given the test statistic and p-value, we *`r params$outcome`* the null hypothesis.
